LAPOR! EDA by Septi Rito Tombe
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
install.packages("ggplot2") 
install.packages("knitr")
install.packages("dplyr")
install.packages('gridExtra')
install.packages('map')
install.packages('lubridate')
install.packages('anytime')
install.packages("grid")
install.packages('GGally')
install.packages('psych')
library(ggplot2)
library(knitr)
library(dplyr)
library(gridExtra)
library(ggmap)
library(lubridate)
library(anytime)
library(grid)
library(GGally)
library(psych)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
df <- read.csv('data/total.csv') 
```
# Introduction
This data fetched from http://data.go.id/dataset/data-aspirasi-dan-pengaduan-masyarakat. It contains reports from Indonesian citizens by a platform called LAPOR!. This platform enables the officials to solve public issues that posted by citizens and it also inform the citizen if the issue was solved. Originally, the data was consist of two csvs, the first csv (data.csv) contains the report's content and its attributes such as creator, area, and category. The other csv (daftararea.csv), contains the area details including its latitude and longitude. Eventually, the csvs was merged based on "area" as shown in the *wrangle.R* file. However, some attributes were **deleted** because it contains redundancy with the other attributes or may contains sensitive materials, such attribute is the report's content.

The rationale behind this data is to explore the usage of the platform. Some questions may be answered through the analysis such as:
1. When is the reports most frequently posted?
2. Proportion of solved reports.
3. Where are mostly the reports originated?
4. etc... (I intent to create 5W + 1H questions as necessary as possible while exploring the data)

This report will contain four main sections. The first three section will contain univariate, bivariate, and multivariate data exloration. Finally, the last section will summarise all the findings and present a reflection. 

# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

```{r echo=FALSE, Univariate_Plots}
dim(df)
```
```{r echo=FALSE, Univariate_Plots}
str(df)
```

```{r echo=FALSE, Univariate_Plots}
summary(df)
```

Below are the histograms of the dataset

```{r echo=FALSE, Univariate_Plots}
df.group_by_status <- group_by(df, status)

df.status_count <- summarise(df.group_by_status,
                             n = n(),
                             proportion = round(n()/nrow(df.group_by_status)*100,3))

#https://www.statmethods.net/graphs/pie.html
labels <- paste(c("Waiting", "In Progress", "Finished"), df.status_count$proportion)
labels <- paste(labels, "%", sep=" ")
pie(df.status_count$n, labels = labels, main = "Report Status Proportion")
```

As shown in the chart, the reports are mostly finished (Selesai) and less than 1% is still waiting to be processed. I wonder, when are these reports issued.

```{r echo=FALSE, Univariate_Plots}
#https://stackoverflow.com/questions/17496358/r-help-converting-factor-to-date
#https://stackoverflow.com/questions/22603847/how-to-extract-month-from-date-in-r
#https://stackoverflow.com/questions/13456241/convert-unix-epoch-to-date-object
df$report_issued.month <- month(anydate(df$report_issued))
df$report_issued.year <- year(anydate(df$report_issued))
df$report_issued.day <- weekdays(anydate(df$report_issued))

not_processed <- subset(df, status == 'Belum')

q1 <- qplot(data = df, x = report_issued.month, binwidth = 1, color = I('white'))+
  scale_x_continuous(breaks = seq(1, 12, 1))

q2 <- qplot(data = df, x = report_issued.year, binwidth = 1, color = I('white') )+
  scale_x_continuous(breaks = seq(2009, 2016, 1))

q3 <- qplot(data = df, x = report_issued.day, color = I('white')) +
  scale_x_discrete(limits =  c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday'))

q4 <- qplot(data = not_processed, x = report_issued.month, binwidth = 1, color = I('white'))+
  scale_x_continuous(breaks = seq(1, 12, 1))

q5 <- qplot(data = not_processed, x = report_issued.year, binwidth = 1, color = I('white') )+
  scale_x_continuous(breaks = seq(2009, 2016, 1))

q6 <- qplot(data = not_processed, x = report_issued.day, color = I('white')) +
  scale_x_discrete(limits =  c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday'))

grid.arrange(textGrob("All Status"), q1, q2, q3, textGrob("Waiting"), q4, q5, q6, ncol = 4, top = "Number of Reports Issued (Issue Time)" )
```

As shown on the histograms above, there are some similarities and differences between the overall status and the waiting data. The similarities can be found in monthly and daily basis, such as the highest report issued in January and least reports issued on weekends. In the other hand, on yearly basis it shows the graphs are contradicted. This make me wonder how long it typically an issue to be solved? I will cover this in Bivariate section.

Furthermore, lets check another time series variables. Such last activity, I wonder how long typically an acitvity being idle/processed (report_last_activity != report_closed).

```{r echo=FALSE, Univariate_Plots}
df$idle_time <- df$report_last_activity - df$report_issued

df$idle_time.month <- df$idle_time/60/60/24/30

df$idle_time.day <- df$idle_time/60/60/24

q1 <- qplot(data =  subset(df, report_closed != report_last_activity), x = idle_time.month,  binwidth = 1, color =  I("white")) + 
  scale_x_continuous(limits = c(0,quantile(df$idle_time.month, 0.99)), breaks = seq(0,quantile(df$idle_time.month, 0.99), 1)) +
  labs(title = "Waiting/Processing Time (monthly basis)", x = "number of month(s)")

q2 <- qplot(data =  subset(df, report_closed != report_last_activity), x = idle_time.day, binwidth = 5, color = I("white")) +
  scale_x_continuous(limits = c(0,quantile(df$idle_time.day, 0.99))) + 
  labs(title = "Waiting/Processing Time (daily basis)", x = "number of day(s)")

grid.arrange(q1, q2)
```
The histogram is highly skewed showing that time for waiting to be processed/processed time is relatively low. However, there are outliers indicated by longtail to be investigated.

```{r echo=FALSE, Univariate_Plots}
summary(subset(df$idle_time.day, df$idle_time.day >= 0))
```

I want to investigate the report_closed, when mostly the reports finished.

```{r echo=FALSE, Univariate_Plots}
df$report_closed.month <- month(anydate(df$report_closed))
df$report_closed.year <- year(anydate(df$report_closed))
df$report_closed.day <- weekdays(anydate(df$report_closed))


q1 <- qplot(data = df, x = report_closed.month, binwidth = 1, color = I('white'))+
  scale_x_continuous(breaks = seq(1, 12, 1))

q2 <- qplot(data = df, x = report_closed.year, binwidth = 1, color = I('white') )+
  scale_x_continuous(breaks = seq(2009, 2016, 1))

q3 <- qplot(data = df, x = report_closed.day, color = I('white')) +
  scale_x_discrete(limits =  c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday'))

grid.arrange(q1, q2, q3, top = "Number of Reports Closed (Issue Time)" )
```

As shown, there are some unusual distribution on the daily histogram, lowest activity presented in Friday and Saturday. In contrast, In general in Indonesia, weekend are Saturday and Sunday. The monthly data shows that mostly reports closed in March and November.

# Univariate Analysis

### What is the structure of your dataset?
The data consists of 79565 reports in 2012-2015. Originally, the data consist of 11 features; eventually, the data expanded to 17 features.

### What is/are the main feature(s) of interest in your dataset?
The main features of the data is the report is the *status*, *area*, and the time series (*report_issued*, *report_last_activity*, and *report_closed*). I intend to investigate areas that have best response in time and finished rate. Furthermore, I also want to investigate the same thing with the *related_department*

### What other features in the dataset do you think will help support your\investigation into your feature(s) of interest?
Additional features like the duration between issued time vs closed time would be a good feature to answer the questions. Moreover, with latitude and longitude I can visualise the data to be more comprehensive in map.

### Did you create any new variables from existing variables in the dataset?
Yes, I created count of each status to find proportion. I also created some new features regarding the time data. For example, the report_issued.month is purposed to group the data into montly basis. Another example is idle_time indicating duration between report_issued and report_last_activity.

### Of the features you investigated, were there any unusual distributions? \ Did you perform any operations on the data to tidy, adjust, or change the form \ of the data? If so, why did you do this?
There is unusual distribution shown in Waiting status, it is contrasting with the overall status. The waiting status shows the data to be declining; in contrast, the overall data shows to be increasing. Another unusual distribution also found in monthly issued data, it shows mostly reports were issued in January. Another anomaly also shown in reports closed on day basis, it is interesting that there is no reports closed in Saturday but there are some reports closed on Sunday. It is interesting because the reports should closed by the officials that should be not working on Sunday. (However, I still unsure maybe if the user delete the report, it also counted as report closed)

There are some actions was conducted to adjust the data. For example, there are some negative values in the duration timeseries, it might be caused by null values in the one of the feature, thus, in visualisation and summary I limit the data from 0. This was done to reduce confusion in presenting the data. 


# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

Here I want to get insights from factors variables. I have three factor variables that I supposed may have meaning (reporter, category, related_department). Nevertheless, these variables has a high degree of level. Thus, I need to subset it to most common ones (5 or 10 levels) for the sake of readability. To do that, I want to create variables of these factors' levels' counts and sort it descending.

``` {r echo=FALSE, Bivariate_Plots}
df.area_count <- count(df, area)
df.area_count <- df.area_count[order(-df.area_count$n),]
df$area.ordered <- ordered(df$area, levels = df.area_count$area)


df.reporter_count <- count(df, reporter)
df.reporter_count <- df.reporter_count[order(-df.reporter_count$n),]
df$reporter.ordered <- ordered(df$reporter, levels = df.reporter_count$reporter)
df.reporter_count <- df.reporter_count[1:100,]

df.category_count <- count(df, category)
df.category_count <- df.category_count[order(-df.category_count$n),]
df$category.ordered <- ordered(df$category, levels = df.category_count$category)
df.category_count <- df.category_count[1:50,]


df.related_department_count <- count(df, related_department)
df.related_department_count <- df.related_department_count[order(-df.related_department_count$n),]
df.related_department_count <- df.related_department_count[1:10,]
```

```{r echo=FALSE, Bivariate_Plots}
 ggplot(data = subset(df, area %in% df.area_count$area), aes(y = area.ordered, x = idle_time.day)) + 
  geom_point(alpha = .1) +
  scale_x_continuous(breaks = seq(0, 5000, 100))
```

```{r echo=FALSE, Bivariate_Plots}
 ggplot(data = subset(df, category %in% df.category_count$category), aes(y = category.ordered, x = idle_time.day)) + 
  geom_point(alpha = .1) +
  scale_x_continuous( breaks = seq(0, 5000, 50))
```

In regards of the categories, it is interesting that there are some categories that shows high variability in term of duration to finish it. For example (the plot should be enlarged to find all category), Jamkesmas, Raskin, ESDM, and BLSM. It is interesting to find out what the cause of this. Let see another variables.
```{r echo=FALSE, Bivariate_Plots}
ggplot(data = subset(df, reporter %in% df.reporter_count$reporter), aes(y = reporter.ordered, x = idle_time.day)) + 
  geom_point(alpha = .1) +
  scale_x_continuous(breaks = seq(0, 5000, 100))
```
There is something special here for user "6281680xxxx ", it seems his/her report mostly done in a long duration.Let see what is it?

```{r echo=FALSE, Bivariate_Plots}
ggplot(data = subset(df, reporter == '6281680xxxx '), aes(y = reporter.ordered, x = category.ordered)) + 
  geom_jitter(alpha = .5)

subset(df, reporter == '6281680xxxx ')
```
Apparently, there are two categories that may done in long period which are, *Topik Lainnya* (other topic) and *Lingkungan hidup dan penanggulangan bencana* (Enviromental and Disaster Countermeasures), both of them are enlisted as top 10 report category. I think, it because the clarity of the report content so it requires time to determine which department that has to deal with it, or it suppoesed to took long time to finish.

```{r echo=FALSE, Bivariate_Plots}
ggplot(data = subset(df, related_department %in% df.related_department_count$related_department), aes(y = related_department, x = idle_time.day)) + 
  geom_jitter(alpha = .05) +
  scale_x_continuous(limits = c(0, quantile(df$idle_time.day, 0.68)), breaks = seq(0, 30, 1))
```


```{r echo=FALSE, Bivariate_Plots}
ggplot(data = df, aes(y = idle_time.day, x = report_issued.day)) + 
  geom_jitter(alpha = .01) +
  scale_y_continuous(limits = c(0, quantile(df$idle_time.day, 0.68)), breaks = seq(0, 30, 1)) +
  scale_x_discrete(limits =  c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday')) + 
  labs(x = 'Day of the Reports Issued', y = 'Duration of Waiting Time to Finish', title = 'Day Issued vs Duration to Finish')

```

It is interesting that this shows that every weekend there are small amount of reports finished, although there are some which might be urgent reports. However, on most case, reports are done only in one day (see Monday - Thursday), while on Friday, whether they intend to finish it in same day or on Monday after the weekends. Furthermore, on Saturday and Sunday, it seems there is very little report, thus there is no significant number of common duration.

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!